---
title: "Country Flags"
output:
  html_document:
    df_print: paged
    theme: cerulean
    bootstrap: 5
    bootswatch: cerulean
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Country Flags in Data 
In a world that is increasingly interconnected, visual communication plays a critical role in conveying information effectively. One powerful tool in this arsenal is the use of flags in data visualization, particularly when presenting country-level data. Flags serve not just as symbols of national identity but also enhance the clarity and appeal of data presentations. Here’s why incorporating flags into your data analysis, such as with the `tidycountries` package, is so impactful.

### A story using Flags
Imagine you are tasked with preparing a report on the top 10 most populated countries and their demographic characteristics. Using `tidycountries`, you can not only gather essential data but also embed flags to enhance your presentation.

```{r setup}
# Load required libraries
library(tidycountries)
library(dplyr)
library(DT)
library(htmltools)
library(scales)

# Fetch countries information using tidycountries
all_countries <- get_country_info("all")

# Filter the top 5 countries by population
top_10_countries <- all_countries %>% 
  select(common_name, official_name, region, population, flags_svg) %>% 
  distinct(common_name, .keep_all = TRUE) %>%  # Ensure unique entries
  arrange(desc(population)) %>% 
  head(n = 10)

# Function to embed flag images
flag_image <- function(url) {
  as.character(tags$img(src = url, width = 50, height = 30))  # Convert to a character string
}

# Format the population values with commas
top_10_countries$population <- comma(top_10_countries$population)

# Apply the flag_image function to the flags_svg column
top_10_countries$Flag <- lapply(top_10_countries$flags_svg, flag_image)

# Create the interactive table using DT
datatable(
  top_10_countries[, c("Flag", "common_name", "official_name", "population")],
  escape = FALSE,  # Allows HTML rendering
  options = list(
    pageLength = 10,   # Number of rows per page
    columnDefs = list(list(className = 'dt-center', targets = "_all")) # Center align
  ),
  colnames = c("Flag", "Common Name", "Official Name", "Population")
)
```

### A Flag-Focused Presentation

By executing the above code, you create a visually appealing table that showcases the top ten most populated countries. Each country is accompanied by its flag, providing instant recognition and enhancing the overall clarity of your presentation.

